---
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme:
      bg: "#101010"
      fg: "#FDF7F7"
      primary: "#33a597"
      base_font:
        google: "Prompt"
      code_font:
        google: "JetBrains Mono"
runtime: shiny
title: "Affordance Norms"
---
<p>

```{r setup, echo = FALSE, warning = FALSE, include = FALSE}
##load libraries
library(shiny)
library(DT)
library(bslib)
library(shinythemes)

##load datasets here
affordances = read.csv("Data/Affordance Norms.csv")
cues = read.csv("Data/Cue Table.csv")

##use this space to update column headings, round values, etc.
affordances$AFS = format(round(affordances$AFS, digits = 3), nsmall = 3)

colnames(affordances)[1] = "Cue"
colnames(affordances)[2] = "Affordance"

cues$BOI = format(round(cues$BOI, digits = 3), nsmall = 3)
cues$Concrete = format(round(cues$Concrete, digits = 3), nsmall = 3)
cues$SUBTLEX = format(round(cues$SUBTLEX, digits = 3), nsmall = 3)

colnames(cues)[1] = "Cue"
colnames(cues)[3] = "Concreteness"
colnames(cues)[4] = "SUBLTEX-US"

```


## General Overview

This page provides a searchable interface for our affordance norming project. The data is organized into two tables, which provide lexical information about each cue item (Table 1) and normative values assessing affordance properties (Table 2). The final dataset contains affordance responses for 3000 concrete nouns and displays affordance strength values (AFS) and affordance set sizes (AFSS). Please note that if you are downloading this application to run locally via RStudio, you will need to download the entire folder from [GitHub](https://github.com/npm27/Affordance-Shiny). 

**Questions?** Email <nicholas.maxwell@msutexas.edu>

## Cue Properties

Table 1 provides lexical properties for each cue item, including body-object interaction ratings ([Pexman et al., 2019](https://link.springer.com/article/10.3758/s13428-018-1171-z)), concreteness ([Brysbaert et al., 2014](https://link.springer.com/article/10.3758/s13428-013-0403-5)), and SUBLTEX frequency ([Brysbaert & New, 2009](https://link.springer.com/article/10.3758/BRM.41.4.977)).

**Note**: A .csv file containing the full set of cue properties is available for download [here](LINK).

### Column Descriptions

**Cue:** The word presented in the norming task. Participants provided open-ended responses indicating how each cue item could be used (i.e., what actions the presented object afforded).

**Body-Object Interaction (BOI):** Values reported in the *BOI* column assess the ease with which individuals can interact with an object. Higher ratings denote greater ease of interaction. These ratings were taken from Pexman et al. (2019)

**Concreteness:** Measures the degree to which a concept refers to a perceptual, tangible object. Ratings are taken from Brysbaert et al. (2014).

**Frequency:** This value captures frequency of use in everyday language. Values reported in the *frequency* column are derived from the SUBTLEX-US frequency database, which contains frequency estimates for 51 million English words derived from movie and television subtitles (Brysbaert & New, 2009).




### Table 1: Cue Item Lexical Properties {#table1}

```{r cue property table, echo = FALSE}
#####Define UI####
ui = fluidPage(
   div(style = 'overflow-x: scroll', DTOutput("affordance_table")),
   theme = shinytheme("cyborg"),
   
   #change the color of page 
   tags$style(HTML(".dataTables_wrapper .dataTables_length, .dataTables_wrapper .dataTables_filter, .dataTables_wrapper    .dataTables_info, .dataTables_wrapper .dataTables_processing,.dataTables_wrapper .dataTables_paginate .paginate_button, .dataTables_wrapper .dataTables_paginate .paginate_button.disabled {
            color: #33a597 !important;
        }")),
   
   tags$style(HTML('table.dataTable tr.selected td, table.dataTable td.selected {background-color: #33a597 !important;}')),
   ) #fluidpage

server = function(input, output) {
   
   output$affordance_table = renderDT(server = TRUE, {
     
     datatable(cues,
               callback=JS('$("button.buttons-copy").css("background","#33a597"); 
                    $("button.buttons-csv").css("background","#33a597");
                    $("button.buttons-excel").css("background","#33a597");
                    return table;'),
               filter = 'top',
               rownames = FALSE,
               extensions = 'Buttons',
               options = list(
                 dom = 'rtpB',
                 buttons = c('copy', 'csv', 'excel'),
                 paging = FALSE
               ) #close options
               ) #close data table 
     
   }) #close render DT
      
}

# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 550))
```



## Cue-Target Affordance Properties

Table 2 provides options for searching this dataset while also controlling for forward association strength (FAS) and indirect association strength (IAS) values derived from the Small-World of Words project ([De Deyne et al., 2019](https://link.springer.com/article/10.3758/s13428-018-1115-7)). The filtered table can then be downloaded to .csv or.xlsx for further analysis. 

**Note**: You can download a .csv file containing the full set of affordance norms [here](LINK).

### Column Descriptions

**Cue:** The word presented in the norming task. Participants provided open-ended responses indicating how each cue item could be used (i.e., what actions the presented object afforded).

**Target:** Responses to each cue. Items in the *Target* column have been lemmatized. Note that only verb responses are displayed in this table.

**Affordance Strength (AFS):** Values in this column reflect the probability of a specific target being provided as a response to a cue. AFS values were computed by first computing the frequency of each unique response to a cue, which was then divided by the total number of responses the cue received. Higher AFS values indicate a greater liklihood that an object will elicit a specific affordance as an action response. Note that this value only considers *verb* responses, as by nature, affordances reflect action properties.

**Affordance Set-Size (AFSS):** This column displays the total number of unique targets that were provided for each cue. Higher values indicate a greater number of perceived affordances.

**n:** The number of individuals who responded to the cue. While at least 30 participants responded to each cue item, this value varied across items.

### Table 2. Cue-Target Affordance Properties

```{r cue-affordance-table, echo = FALSE}
#####Define UI####
ui = fluidPage(
   div(style = 'overflow-x: scroll', DTOutput("affordance_table")),
   theme = shinytheme("cyborg"),
   #change the color of page 
   tags$style(HTML(".dataTables_wrapper .dataTables_length, .dataTables_wrapper .dataTables_filter, .dataTables_wrapper    .dataTables_info, .dataTables_wrapper .dataTables_processing,.dataTables_wrapper .dataTables_paginate .paginate_button, .dataTables_wrapper .dataTables_paginate .paginate_button.disabled {
            color: #33a597 !important;
        }")),
   
   tags$style(HTML('table.dataTable tr.selected td, table.dataTable td.selected {background-color: #33a597 !important;}')),
   ) #fluidpage

server = function(input, output) {
   
   output$affordance_table = renderDT(server = TRUE, {
     
     datatable(affordances, 
               callback=JS('$("button.buttons-copy").css("background","#33a597"); 
                    $("button.buttons-csv").css("background","#33a597");
                    $("button.buttons-excel").css("background","#33a597");
                    return table;'),
               filter = 'top',
               rownames = FALSE,
               extensions = 'Buttons',
               options = list(
                 dom = 'rtpB',
                 buttons = c('copy', 'csv', 'excel'),
                 paging = FALSE
               ) #close options
               ) #close data table 
     
   }) #close render DT
      
}

# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 550))
```



