---
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme:
      bg: "#101010"
      fg: "#FDF7F7"
      primary: "#33a597"
      base_font:
        google: "Prompt"
      code_font:
        google: "JetBrains Mono"
runtime: shiny
title: "Affordance Norms"
---
<p>

```{r setup, echo = FALSE, warning = FALSE, include = FALSE}
##load libraries
library(shiny)
library(DT)
library(bslib)
library(shinythemes)

##load datasets here
affordances = read.csv("Data/Affordance Norms_fsg.csv")
cues = read.csv("Data/Cue Table.csv")

##use this space to update column headings, round values, etc.
affordances$AFS = format(round(affordances$AFS, digits = 3), nsmall = 3)

colnames(affordances)[1] = "Cue"
colnames(affordances)[2] = "Affordance"

cues$BOI = format(round(cues$BOI, digits = 3), nsmall = 3)
cues$Concrete = format(round(cues$Concrete, digits = 3), nsmall = 3)
cues$SUBTLEX = format(round(cues$SUBTLEX, digits = 3), nsmall = 3)

##fix column names
colnames(cues)[1] = "Cue"
colnames(cues)[4] = "Concreteness"
colnames(cues)[5] = "Frequency"

##fix numeric variables
cues$BOI = as.numeric(cues$BOI)
cues$Concreteness = as.numeric(cues$Concreteness)
cues$Frequency = as.numeric(cues$Frequency)

affordances$AFS = as.numeric(affordances$AFS)

```


## General Overview

This page provides a searchable interface for our affordance norming project. The data is organized into two tables, which provide lexical information about each cue item (Table 1) and normative values assessing affordance properties (Table 2). The final dataset contains affordance responses for 2825 concrete nouns and displays affordance strength values (AFS), affordance set sizes (AFSS), as well as several lexical and semantic variables. Please note that if you are downloading this application to run locally via RStudio, you will need to download the entire folder from [GitHub](https://github.com/npm27/Affordance-Shiny). 

**Questions?** Email <nicholas.maxwell@msutexas.edu>

## Cue Properties

Table 1 provides lexical properties for each cue item, including body-object interaction ratings (*BOI*; [Pexman et al., 2019](https://link.springer.com/article/10.3758/s13428-018-1171-z)), *concreteness* ([Brysbaert et al., 2014](https://link.springer.com/article/10.3758/s13428-013-0403-5)), *SUBLTEX frequency* ([Brysbaert & New, 2009](https://link.springer.com/article/10.3758/BRM.41.4.977)), and age-of-acquisition (*AOA*; [Kuperman et al., 2012](https://link.springer.com/article/10.3758/s13428-012-0210-4)), and the number of participants who responded to each cue in our dataset (*n*).

<span style="color:#33a597">**Note:**</span> A .csv file containing the full set of cue properties is available for download [here](https://github.com/npm27/Affordance-Shiny/blob/main/Cue%20Table.csv). The data can also be downloaded or copied to the clipboard using the buttons located at the bottom of the table.

### Column Descriptions

<span style="color:#33a597">**Cue:**</span> The word presented in the norming task. Participants provided open-ended responses indicating how each cue item could be used (i.e., what actions the presented object afforded).

<span style="color:#33a597">**Affordance Set Size (AFSS):**</span> *AFSS* values denote the total number of unique affordances elicited for each cue.

<span style="color:#33a597">**Body-Object Interaction (BOI):**</span> Values reported in the *BOI* column assess the ease with which individuals can interact with an object. Higher ratings denote greater ease of interaction. These ratings were taken from Pexman et al. (2019)

<span style="color:#33a597">**Concreteness:**</span> *Concreteness* ratings measure the degree to which a concept refers to a perceptual, tangible object. Values in this column are derived from Brysbaert et al. (2014).

<span style="color:#33a597">**Frequency:**</span> This value captures frequency of use in everyday language. Values reported in the *frequency* column are derived from the SUBTLEX-US frequency database, which contains frequency estimates for 51 million English words derived from movie and television subtitles (Brysbaert & New, 2009).

<span style="color:#33a597">**Age of Acquisition (AoA):**</span> *AoA* reflects the average age at which a word is learned. Values reported in this column are take from Kuperman et al. (2012).

<span style="color:#33a597">**Length:**</span> The *Length* column denotes the total number of characters in each cue word.

<span style="color:#33a597">**n.unique:**</span> This column displays the total number of participants who responded to each cue item in the affordance dataset.

<span style="color:#33a597">**n.unique.affordance:**</span> Values in this column reflect the number of participants who provided at least one **affordance response (e.g., action)** to each cue item.

<span style="color:#33a597">**total.affordance:**</span> The total number of affordances provided for each cue. This value includes multiple uses provided by the same participant

### Table 1: Cue Item Lexical Properties {#table1}

```{r cue property table, echo = FALSE}
#####Define UI####
ui = fluidPage(
   div(style = 'overflow-x: scroll', DTOutput("affordance_table")),
   theme = shinytheme("cyborg"),
   
   #change the color of page 
   tags$style(HTML(".dataTables_wrapper .dataTables_length, .dataTables_wrapper .dataTables_filter, .dataTables_wrapper    .dataTables_info, .dataTables_wrapper .dataTables_processing,.dataTables_wrapper .dataTables_paginate .paginate_button, .dataTables_wrapper .dataTables_paginate .paginate_button.disabled {
            color: #33a597 !important;
        }")),
   
   tags$style(HTML('table.dataTable tr.selected td, table.dataTable td.selected {background-color: #33a597 !important;}')),
   ) #fluidpage

server = function(input, output) {
   
   output$affordance_table = renderDT(server = TRUE, {
     
     datatable(cues,
               callback=JS('$("button.buttons-copy").css("background","#33a597"); 
                    $("button.buttons-csv").css("background","#33a597");
                    $("button.buttons-excel").css("background","#33a597");
                    return table;'),
               filter = 'top',
               rownames = FALSE,
               extensions = 'Buttons',
               options = list(
                 dom = 'rtpB',
                 buttons = c('copy', 'csv', 'excel'),
                 paging = FALSE
               ) #close options
               ) #close data table 
     
   }) #close render DT
      
}

# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 550))
```



## Cue-Target Affordance Properties

Table 2 displays the full affordance norms dataset and provides options for searching and filtering the dataset. The filtered table can be downloaded to .csv or.xlsx for further analysis. Forward strength (FSG) values derived from ([Nelson et al., 2004](https://link.springer.com/article/10.3758/BF03195588)) and cosine values (COS) taken from ([Buchanan et al., 2019](https://link.springer.com/article/10.3758/s13428-019-01243-z)) are provided when available.

<span style="color:#33a597">**Note:**</span> You can download a .csv file containing the full set of affordance norms [here](https://github.com/npm27/Affordance-Norms/blob/main/4%20Analyses/R/Affordance%20Norms.csv). The data can also be downloaded or copied to the clipboard using the buttons located at the bottom of the table.

### Column Descriptions

<span style="color:#33a597">**Cue:**</span> The word presented in the norming task. Participants provided open-ended responses indicating how each cue item could be used (i.e., what actions the presented object afforded).

<span style="color:#33a597">**Target:**</span> The affordance response to each cue. Items in the *Target* column have been lemmatized. Note that only verb responses are displayed in this table.

<span style="color:#33a597">**Affordance Strength (AFS):**</span> Values in this column reflect the probability of a specific target being provided as a response to a cue. AFS values were computed by first computing the frequency of each unique affordance response to a cue, which was then divided by the total number of responses the cue received. Higher AFS values indicate a greater likelihood that an object will elicit a specific affordance as an action response. Note that this value only considers *verb* responses, as by nature, affordances reflect action properties.

<span style="color:#33a597">**Affordance Percentage (AFP):**</span> This column denotes the percentage of participants who responded to each cue with a given affordance. AFP values were calculated by computing the frequency of each unique affordance response and dividing by the total number of participants who responsed to the cue. Higher AFP values denote a greater percentage of participants who provided the affordance. Like AFS, AFP was calculated using *verb* responses only.

<span style="color:#33a597">**Forward Strength (FSG):**</span> Values in this column denote forward strength values taken from the University of South Florida Free Association Norms (Nelson et al., 2004). *FSG* measures the association between cue and target in terms of response probabilities. Higher values denote a greater probability of target being elicited as a response.

<span style="color:#33a597">**Cosine (COS):**</span> This column contains *COS* values taken from Buchanan et al.'s (2019) feature production norms. This value represents the degree of semantic similarity between two items.

### Table 2: Cue-Target Affordance Properties {#table2}

```{r cue-affordance-table, echo = FALSE}
#####Define UI####
ui = fluidPage(
   div(style = 'overflow-x: scroll', DTOutput("affordance_table")),
   theme = shinytheme("cyborg"),
   #change the color of page 
   tags$style(HTML(".dataTables_wrapper .dataTables_length, .dataTables_wrapper .dataTables_filter, .dataTables_wrapper    .dataTables_info, .dataTables_wrapper .dataTables_processing,.dataTables_wrapper .dataTables_paginate .paginate_button, .dataTables_wrapper .dataTables_paginate .paginate_button.disabled {
            color: #33a597 !important;
        }")),
   
   tags$style(HTML('table.dataTable tr.selected td, table.dataTable td.selected {background-color: #33a597 !important;}')),
   ) #fluidpage

server = function(input, output) {
   
   output$affordance_table = renderDT(server = TRUE, {
     
     datatable(affordances, 
               callback=JS('$("button.buttons-copy").css("background","#33a597"); 
                    $("button.buttons-csv").css("background","#33a597");
                    $("button.buttons-excel").css("background","#33a597");
                    return table;'),
               filter = 'top',
               rownames = FALSE,
               extensions = 'Buttons',
               options = list(
                 dom = 'rtpB',
                 buttons = c('copy', 'csv', 'excel'),
                 paging = FALSE
               ) #close options
               ) #close data table 
     
   }) #close render DT
      
}

# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 550))
```



